### 2016-05-22 w-wires/paper_gerasimovda.tex
Prettified the paper

@@

\section*{Proof of completeness for $a = b = 0$}
Under the substitituion $a = 0, b = 0$, $\det S$ simplifies to:

@@

% We'll use the inequality:

% \[
% \frac{x}{1 + x} \le \ln(1 + x)
% \]
% , which holds for $-1 < x \le 0$. % As $x$ goes to $-1$,

% We'll rewrite it in a more convenient form by a substitution $x \to s(k) - 1$:

% \[
% 1 - \frac{1}{s(k)} \le \ln s(k)
% \]

% Since $s(k)$

\subsection{Upper bound for integral}

We know that $s(k)$ is bounded by $1$ from above in the upper complex plane  ($\Im k \ge 0$) \todo{why?}, hence $\ln \abs{\det S} \le 0$ and the desired integral is bounded from above by $0$. However, we have to show that the integral is bounded from below as well. So, next, we will compute a lower bound $l(k)$ for $s(k)$, such that $0 \le l(k) \le s(k)$, and will prove that $\int \ln l(k)$ converges to $0$. Since $\ln l(k) \le \ln s(k)$, that will prove convergence of the original integral.

\subsection{Notice that $s(k)$ is periodic w.r.t. real axis}
\todo{Plot of $\abs{\det S}$ ?}

% Since $\sin k$ and $\cos k$ are periodic w.r.t the real axis, with the period of $2 \pi$, 
\todo{is this step really necessary?}

Notice that all zeroes have $\Im k = \atanh \frac{2 W}{W^2 + 1}$. For brevity, let's define $Z = \atanh \frac{2 W}{W^2 + 1}$.

\subsection{Notice that for any $x$, $s(x + \iu y) \le s(\iu y)$}
\todo{How to prove? We could probably take a look at numerator and denominator in separate?}

@@

\[
s_1(x + \iu y)
 = \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}}
\]
, now that $\cosh y \ge 1$, we are free to divide by $\cosh y$:

\[
s_1(x + \iu y)
 = \abs{\frac{\tanh y - \frac{2 W}{W^2 + 1}}{\tanh y + \frac{2 W}{W^2 + 1}}}
\]

Note that now $s_1(k)$ has zeroes along the line $\Im k = Z = \atanh \frac{2 W}{W^2 + 1}$, which means $\ln s_1(k)$ will have continuous number of singularities along this line, whereas the original function $\ln\abs{\det S(k)}$ only had countable number of singularities. However, we'll show that the function is still integrable.

@@

\subsection*{Case 1: $0 \le y \le Z$}
Since denominator $\tanh y + \frac{2 W}{W^2 + 1}$ only increases as $0 \le y \le Z$, we can replace it with its maximum value $\tanh Z + \frac{2 W}{W^2 + 1} = \frac{4 W}{W^2 + 1}$, thus getting estimate $s_2$:

@@

\subsection*{Case 2: $y > Z$}
For $y > Z$, 
\[
s_1(x + \iu y) 
 = \frac{\tanh y - \frac{2 W}{W^2 + 1}}{\tanh y + \frac{2 W}{W^2 + 1}}
 = 1 - 2 \frac{\frac{2 W}{W^2 + 1}}{\tanh y + \frac{2 W}{W^2 + 1}}
\]

% TODO
% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
Since $s_1$ is concave \todo{proof? just take a look at second derivative?}, and strictly increasing, we can take any $Z_0 > Z$ and approximate the function by a piecewise linear function $s_4$.

\[
s_4(x + \iu y) = 
\begin{cases}
\frac{s_1(Z_0)}{Z_0 - Z} (y - Z) &, Z < y \le Z_0 \\
s_1(Z_0) &, y > Z_0
\end{cases}
\]

For simplicity, take $Z_0 = Z + 1$, then:

\[
s_4(x + \iu y) = 
\begin{cases}
s_1(Z + 1) (y - Z) &, Z < y \le Z + 1 \\
s_1(Z + 1) &, y > Z + 1
\end{cases}
\]

\subsection*{Proof of convergence for constant part}
\todo{Might be easier in Cayley space}

@@

Not than we have an estimate for $s(k)$ on the whole upper complex plane, we can compute the lower bound for the original integral. For fixed $r$ (radius of the contour in Cayley space), the integral looks like:

\[
\int\limits_{C_r} \ln l(k) \frac{1}{(k + i)^2} dk
\]

, where $C_r$ is the image of the curve $\abs{\zeta} = r$ under the inverse Cayley transform.

Cayley transform: $W(z) = \frac{z - \iu}{z + \iu}$, inverse: $w(\zeta) = \iu \frac{1 + \zeta}{1 - \zeta}$.

$C_r$ is the circle with radius $R(r) = \Im \frac{w(r) - w(-r)}{2}$ and center $C(r) = \Im \frac{w(r) + w(-r)}{2}$.

Substituting $k \to R \eexp{\iu t} + \iu C$, we get:

\todo{multiply by $2 \iu$ due to derivative of Cayley transform}

\[
\int\limits_{0}^{2 \pi} \ln l(R \eexp{\iu t} + \iu C) \frac{1}{(R \eexp{\iu t} + \iu C + i)^2} R \iu dt
\]

To estimate this integral, we'll use Cauchy-Schwartz inequality:

To make use of the inequality, we take
\begin{align*}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln l(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \iu \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{align*}

\subsection*{Estimate of $\int \abs{g(t)}^2$}

If we take $a = R + (C + 1) \frac{C + 1}{R}$, $b = 2 (C + 1)$, and notice $a > b$ \todo{Prove}, the integral is well known \todo{reference}:
\[
\int \frac{dx}{a + b \sin x} = \frac{2}{\sqrt{a^2 - b^2}} \atan \frac{a \tan \frac{x}{2} + b}{\sqrt{a^2 - b^2}}
\]

Now, since $\frac{2}{\sqrt{a^2 - b^2}} \le \frac{2}{2} = 1$ and $\atan$ is bounded by $\frac{\pi}{2}$, by direct application of the fact above, we conclude that than $\pi$.

>>>>

\section{Convergence criterion}

In the Cayley space, the \todo{name} criterion is:
\[
\lim\limits_{r \to 1} \int\limits_{\abs{\zeta} = r} \ln \abs{\det S(\zeta)} d\zeta = 0
\]

Since $S$-matrix is naturally defined on the complex plane, it is easier work in the upper complex plane. To do that, we apply the Cayley transorm $W(z) = \frac{z - \iu}{z + \iu}$, which maps upper complex plane to the unit disk, and its inverse $w(\zeta) = \iu \frac{1 + \zeta}{1 - \zeta}$, which yields:

\begin{equation}\label{crit}
\lim\limits_{r \to 1} \int\limits_{C_r} \ln \abs{\det S(k)} \frac{2 \iu}{(k + i)^2} dk = 0
\end{equation}

, where $C_r$ is the image of the curve $\abs{\zeta} = r$ under the inverse Cayley transform. Since Cayley transform is a Mobius transformation and preserves circles, $C_r$ will actually be a circle with radius $R(r) = \Im \frac{w(r) - w(-r)}{2}$ and center $C(r) = \Im \frac{w(r) + w(-r)}{2}$.

Fox the computational convenience, it $C_r$ is parameterized via $k = R(r) \eexp{\iu t} + \iu C(r)$, which yields us the final form of the criterion, which we will use further:

\begin{equation}\label{critp}
\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln \abs{\det S(R(r) \eexp{\iu t} + \iu C(r))} \frac{2 \iu}{(R(r) \eexp{\iu t} + \iu C(r) + i)^2} R \iu dt = 0
\end{equation}

\section{Model}

@@

\section{Proof of completeness for $a = b = 0$}
Under the substitituion $a = 0, b = 0$, $\det S$ simplifies to:

@@

We know that $s(k)$ is bounded by $1$ from above in the upper complex plane  ($\Im k \ge 0$) \todo{why?}, hence $\ln \abs{\det S} \le 0$ and the desired integral is bounded from above by $0$. However, we have to show that the integral is bounded from below as well. To do that, for each $r$ we will compute a lower bound $L_r(k)$ for the integral under the limit, and will prove that $\lim\limits_{r \to 1} L_r(k) = 0$.

\section{Estimation of integral for fixed $r$}

To compute the estimate, we will use the Cauchy-Schwartz inequality:

To make use of the inequality, we split the integrand of (\ref{critp}) into $f(t) g^*(t)$:
\begin{align*}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \iu \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{align*}
\todo{Multiply $g^*(t)$ by 2 $\iu$}. Next, we will show that $\int \abs{g(t)}^2$ has an upper bound independent of $r$, and $\int \abs{f(t)}^2$ converges to $0$ as $r$ goes to $1$, which immediately proves the convergence to zero.

\subsection{Estimate of $\int \abs{g(t)}^2$}

If we take $a = R + (C + 1) \frac{C + 1}{R}$, $b = 2 (C + 1)$, and notice $a > b$ \todo{Prove}, the antiderivative is well known \todo{reference}:
\[
\int \frac{dx}{a + b \sin x} = \frac{2}{\sqrt{a^2 - b^2}} \atan \frac{a \tan \frac{x}{2} + b}{\sqrt{a^2 - b^2}}
\]

Now, since $\frac{2}{\sqrt{a^2 - b^2}} \le \frac{2}{2} = 1$ and $\atan$ is bounded by $\frac{\pi}{2}$, by direct application of the fact above, we conclude that the integral is less than $\pi$.

\subsection{Estimate of $\int \abs{f(t)}^2$}

First, we will compute a lower bound $l(k)$ for $s(k)$, such that $0 \le l(k) \le s(k)$. Then, we replace $s(k)$ with its lower bound under the integral sign and will prove convergence of this integral to $0$. This reasoning is valid since for $s(k) \le 1$, $\ln l(k) \le \ln s(k)$.

\subsubsection{Computing $s(k)$}
First, notice that $s(k)$ is periodic w.r.t. real axis.
\todo{Plot of $\abs{\det S}$ ?}
% Since $\sin k$ and $\cos k$ are periodic w.r.t the real axis, with the period of $2 \pi$, 
\todo{is this step really necessary?}

$s(k)$ has countable number of zeros, all with $\Im k = \atanh \frac{2 W}{W^2 + 1}$. For brevity, let's define $Z = \atanh \frac{2 W}{W^2 + 1}$.

Notice that for any $x$, $s(x + \iu y) \le s(\iu y)$
\todo{How to prove? We could probably take a look at numerator and denominator in separate?}

@@

\begin{align*}
s_1(x + \iu y)
 &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}} && \text{(since $\cosh y \ge 1$)}\\
 &= \abs{\frac{\tanh y - \frac{2 W}{W^2 + 1}}{\tanh y + \frac{2 W}{W^2 + 1}}}
\end{align*}

Note that now $s_1(k)$ has zeroes along the line $\Im k = Z = \atanh \frac{2 W}{W^2 + 1}$, which means $\ln s_1(k)$ will have continuous number of singularities along this line. However, we'll show that the function is still integrable.

@@

\subsubsection*{Case 1: $0 \le y \le Z$}
Since denominator $\tanh y + \frac{2 W}{W^2 + 1}$ only increases as $0 \le y \le Z$, we can replace it with its maximum value $\tanh Z + \frac{2 W}{W^2 + 1} = \frac{4 W}{W^2 + 1}$, thus getting estimate $s_2$:

@@

\subsubsection*{Case 2: $y > Z$}
For $y > Z$, 
\[
s_1(x + \iu y) 
 = \frac{\tanh y - \frac{2 W}{W^2 + 1}}{\tanh y + \frac{2 W}{W^2 + 1}}
 = 1 - 2 \frac{\frac{2 W}{W^2 + 1}}{\tanh y + \frac{2 W}{W^2 + 1}}
\]

% TODO
% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
Since $s_1$ is concave \todo{proof? just take a look at second derivative?}, strictly increasing and for fixed $r$, our domain of interest is only $\Im k \le C + R$, we can approximate the function by a linear function $s_4$.

\[
s_4(x + \iu y) = 
\frac{s_1(C + R)}{C + R - Z} (y - Z)
\]

@@
